Deciding Bitvector Termination with Program Synthesis

### 2014-07-06 papers/termination/paper.tex
remove italic font in related work

Key: \tick = terminating, \xmark = non-terminating.

@@

Given the lack of research in handling \emph{not-linear programs}, as well
as \emph{programs over bit vectors and floats}, our work focused on covering
these areas.  One of the obvious conclusions that can be reached from
observing Figure~\ref{fig:handletable}, is that most of the works tend to
specialise on a certain aspect of termination proving that they can solve
efficiently.  Conversely to this view, we aim for \emph{generality}, as we
do not restrict the form of the synthesised ranking functions, nor the form
of the input programs.

>>>>

Key: \tick = terminating, \xmark = non-terminating, ? = unknown (tool terminated with an inconclusive verdict).

@@

Given the lack of research in handling not-linear programs, as well
as programs over bit vectors and floats, our work focused on covering
these areas.  One of the obvious conclusions that can be reached from
observing Figure~\ref{fig:handletable}, is that most of the works tend to
specialise on a certain aspect of termination proving that they can solve
efficiently.  Conversely to this view, we aim for generality, as we
do not restrict the form of the synthesised ranking functions, nor the form
of the input programs.
